---
title: "Assignment"
author: "Gurjot Singh"
date: "21 6 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown and Leaflet

## Introduction

Leaflet is one of the most popular Javascript libraries for creating interactive maps. The leaflet R package allows you to create your own leaflet maps without needing to know any Javascript!


## My First Map

Getting started with leaflet is easy. The leaflet() function creates a map widget that you can store in a variable so that you can modify the map later on. You can add features to the map using the pipe operator (%>%) just like in dplyr. The addTiles() function adds mapping data from Open Street Map.

```{r , echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
    addTiles()
my_map
```

## Adding Markers

You can add markers to your map one at a time using the addMarkers() function by specifying the longitude and latitude. (Here’s a tip if you tend to mix them up.) You can specify popup text for when you click on the marker with the popup argument.

```{r}
my_map <- my_map %>% 
    addMarkers(lat = 53.5511, lng = 9.9937,
               popup = "My Home Town Hamburg")
my_map
``` 